---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# moodleLA

<!-- badges: start -->

[![Repostatus: WIP](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://lifecycle.r-lib.org/reference/figures/lifecycle-experimental.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/moodleLA)](https://CRAN.R-project.org/package=moodleLA)
[![R-CMD-check](https://github.com/bfisseler/moodleLA/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bfisseler/moodleLA/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/bfisseler/moodleLA/graph/badge.svg)](https://app.codecov.io/gh/bfisseler/moodleLA)
<!-- badges: end -->

The goal of moodleLA is to facilitate access to and manipulating of Moodle&trade; data for learning analytics practitioners. Moodle is a widely used open source learning management system (LMS). For more information about Moodle go to [www.moodle.org](https://moodle.org/). 

## Credits

This package is developed and maintained by Björn Fisseler from University of Hagen (FernUniversität in Hagen).

## Installation

To install the latest development version:

```{r, eval=FALSE}
devtools::install("bfisseler/moodleLA")
```
